---
title: "Dark Rates in European Cartels"
author: '@bellni'
date: "March 04, 2020"
header-includes:
   - \usepackage{bbm}
   - \usepackage{subfig}
   - \usepackage{dcolumn}
   - \usepackage{amsthm}
   - \usepackage{amsmath}
   - \usepackage[authoryear]{natbib}

output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
With the aim to identify shortcomings of Hazard Rate models in estimating population 
sizes of cartels and supporting our new statistical method, we generate a dgp based on 
the classic work on collusion dating back to \citet{Stigler:1964}.\footnote{Our general model 
does not discriminate between explicit and tacit collusion. In particular, the model does not 
require communication between the parties. See \citet{Ivaldi:Jullien:Rey:Seabright:Tirole:2003} 
we use and add Woodpulp Case and state that US difference.} 
We generate a dgp understanding formation, detection and dissolution of cartels. We start by 
simulating a simple workhorse model of collusion to derive an entire population of cartels 
and two subsamples. In the first sample of uncovered cartels, we do not introduce structure 
over time i.e. {\it unstructured}. In the second sample, repeat offenders have a higher 
likelihood of being detected by a CA and applying for Leniency  i.e. {\it structured}. 


## Summary Plots

```{r, echo=FALSE, fig.align="center", out.width='0.65\\linewidth', fig.cap="My caption"}
knitr::include_graphics("../../out/figures/caught_cartels.pdf")
```

In general, we define collusion in the classic framework; i.e. a market conduct that 
enables firms to obtain supra-normal profits, where normal profits correspond to the 
competitive equilibrium. Consequently, firms may set and maintain higher prices by 
(tacitly) agreeing that any deviation from the collusive path would trigger some retaliation. 
Retaliation must be sufficiently likely and costly to outweigh the short-term benefits from 
cheating on the collusive path. These short-term benefits, as well as the magnitude and 
likelihood of retaliation, depend in turn on the characteristics of the industry. 


## Regression Table

To be effective, retaliation must imply a significant profit loss for the deviating firm, 
compared with the profit that it would have obtained by sticking to the collusive path. 
A simple form of retaliation consists in the breakdown of collusion and the restoration 
of competition and competitive profits. Firms then anticipate that collusive prices will 
be maintained as long as none of them deviates, but if one attempts to reap short-term 
profits by undercutting prices, they will be no more collusion in the future. This form of 
collusion has a simple interpretation: firms trust each other to maintain collusive prices; 
but if one of them deviates, trust vanishes and all firms start acting in their short-term 
interest. 

\input{../../out/tables/regression_table.tex}

Many characteristics can affect the sustainability of collusion 
(\citet{Suslow:Levenstein:2011} and \citet{Stigler:1964}). 
First, there are some basic market specific variables; number of competitors, entry/exit barriers, 
firm interaction, and market transparency. Second, there are characteristics 
about the demand side; i.e. market growth, demand fluctuations or business cycles. 
Third, there are characteristics about the supply side; i.e. technology change, 
innovation, firm symmetry (e.g. homogeneous goods, production costs and production). 
In our simple model, we choose the number of firms to determine crucial cut-off 
levels for the discount factor, determining cartel formation and cheating by cartel members, 
leading to dissolution \citet{Stigler:1964}.

% BEGIN REFERENCES
\newpage
\bibliography{Proposal}
\bibliographystyle{apalike}